Compositional Quantitative Resource Analysis of C Programs

### 2014-06-21 paper/main.tex
add binary counter increment in the logic

\begin{figure}
\begin{lstlisting}
${\color{blue} \{ A(0, N) + N \} }$
i=1; m=a[0];
${\color{blue}%
  \{ (i {=} 1 \land m=a[0]) + A(1, N) + (N-1) \} }$
while (i<N) {
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i-1]} a[k]) + A(i, N) + (N-i) \} }$
  if (a[i] > m)
    m = a[i];
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i]} a[k]) + A(i+1, N) + (N-i) \} }$
  i = i+1;
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i-1]} a[k]) + A(i, N) + (N-i) \} }$
}
${\color{blue} \{ 0 \} }$
\end{lstlisting}
\caption{Example derivation where we noted $A(i, N)$
  for $\#\{ k \mid i \le k \le N \land \forall\, 0\le j<k.\, a[j] < a[k]\}$}
\label{fig:exemple}
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}
${\color{blue} \{ A(0, N) + N \} }$
i=1; m=a[0];
${\color{blue}%
  \{ (i {=} 1 \land m=a[0]) + A(1, N) + (N-1) \} }$
while (i < N) {
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i-1]} a[k]) + A(i, N) + (N-i) \} }$
  if (a[i] > m)
    m=a[i];
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i]} a[k]) + A(i+1, N) + (N-i) \} }$
  i=i+1;
  ${\color{blue}%
    \{ (m = \max_{k \in [0, i-1]} a[k]) + A(i, N) + (N-i) \} }$
} ${\color{blue} \{ 0 \} }$
\end{lstlisting}
\caption{Example derivation where we noted $A(i, N)$
  for $\#\{ k \mid i \le k \le N \land \forall\, 0\le j<k.\, a[j] < a[k]\}$,
  the metric used here assigns a cost of 1 to every assignment
  and 0 to all other operations.
  }
\label{fig:xmplmax}
\end{figure}

\begin{figure}
\begin{lstlisting}
${\color{blue}%
  \{ \#_1(a) + 2k \}}$
while (k > 0) {
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
  while (a[x] == 1 && x < N) {
    ${\color{blue}%
      \{ (a[x] = 1) + \#_1(a) + 2k \}}$
    a[x]=0;
    ${\color{blue}%
      \{ (a[x] = 0) + \#_1(a) + 2k + 1 \}}$
    tick(1);
    ${\color{blue}%
      \{ \#_1(a) + 2k \}}$
    x++; }
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
  if (x < N) {
    ${\color{blue}%
      \{ \#_1(a) + 1 + 2(k-1) + 1 \}}$
    a[x]=1;
    ${\color{blue}%
      \{ \#_1(a) + 2(k-1) + 1 \}}$
    tick(1); }
  ${\color{blue}%
    \{ \#_1(a) + 2(k-1) \}}$
  k--;
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
} ${\color{blue} \{ 0 \}}$

\end{lstlisting}
\caption{Exemple derivation using amortized reasoning, we noted
  $\#_1(a)$ for $\# \{ i \mid 0 \le i < N \land a[i] = 1 \}$, we use the
  tick metric that assigns cost $n$ to \lstinline{tick(n)} statments and
  0 to other operations.
  }
\label{fig:xmplinc}
\end{figure}
